\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{mycol}{HTML}{4B6F44}
\usepackage{parskip}
\usepackage[hidelinks, urlcolor=mycol, colorlinks=true]{hyperref}

% Formatting section headers
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

% No indentation
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Ambrogio Maria Bernardelli}}\\
    \vspace{0.2cm}
     \textsc{Curriculum Vitae et Studiorum}
\end{center}

\vspace{0.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Research Positions}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{01/2025-present}] Postdoctoral researcher, University of Pavia, Department of Mathematics, for the project \emph{Stochastic optimization for electrical energy storage systems and renewable energy sources.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Ph.D. in Computational Mathematics and Decision Sciences \\ \small University of Pavia and Università della Svizzera Italiana} 
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[Cycle:] XXXVII.
    \item[Dates:] 01/2022 -- 12/2024.
    \item[Thesis title:] \emph{Methods for Combinatorial Optimization and Their Applications}.
    \item[Supervisor:] Prof. Stefano Gualandi.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{M.Sc. in Mathematics [LM-40] \\ \small University of Pavia}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[Dates:]  10/2019 -- 09/2021.
    \item[Thesis title:] \emph{Aspetti Algebrici e Combinatori della Teoria degli Operad} (Algebraic and Combinatorial Aspects of Operad Theory).
    \item[Supervisor:] Prof. Alberto Canonaco.   
    \item[Grade:] 110/110 cum laude.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{B.Sc. in Mathematics [L-35] \\ \small University of Pavia}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[Dates:] 10/2016 -- 09/2019.
    \item[Thesis title:] \emph{Rappresentazioni Lineari di Gruppi Finiti} (Linear Representations of Finite Groups).
    \item[Supervisor:] Prof. Alberto Canonaco.
    \item[Grade:] 110/110 cum laude.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conferences Participation}
Conferences and workshops where my works have been presented. Invited talks are labeled with $^\dagger$.
\begin{itemize}[labelwidth=*,align=left, labelwidth=!]
\item[\texttt{06/2026}] IPCO 2026, Padova, Italy. Poster.
    \item[\texttt{09/2025}] The HEXAGON Workshop on power grids, Benevento, Italy$^\dagger$.
    \item[\texttt{09/2025}] ODS 2025, Milan, Italy. 
    \item[\texttt{07/2024}] IPCO 2024, Wrocław, Poland. Poster.
    \item[\texttt{07/2024}] ISMP 2024 (presented by Simone Milanesi), Montréal, Canada$^\dagger$.
    \item[\texttt{06/2024}] EURO 2024 (presented by Simone Milanesi), Copenhagen, Denmark$^\dagger$. 
    \item[\texttt{06/2024}] The HEXAGON Workshop on power grids, Bergamo, Italy$^\dagger$.
    \item[\texttt{05/2024}] ISCO 2024, San Cristóbal de La Laguna, Spain.
    \item[\texttt{10/2023}] 2023 INFORMS Annual Meeting (presented by Stefano Gualandi), Phoenix, Arizona$^\dagger$.
    \item[\texttt{06/2023}] LION17, Nice, France. The work \emph{The BeMi Stardust: a Structured Ensemble of Binarized Neural Network} presented here got accepted for the conference proceedings.
    \item[\texttt{02/2023}] 7th AIROYoung Workshop (presented by Simone Milanesi), Milano, Italy.
    \item[\texttt{02/2023}] 7th AIROYoung Workshop, Milano, Italy.
    \item[\texttt{01/2023}] The Mathematics of Machine Learning (presented by Simone Milanesi), Pisa, Italy.
    \item[\texttt{11/2022}] Matematica per l’Intelligenza Artificiale e il Machine Learning - Giovani ricercatori, Torino, Italy.
    \item[\texttt{09/2022}] YAMC 2022, Arenzano, Italy. 
    \item[\texttt{07/2022}] ICCOPT / MOPTA 2022, Lehigh University, Bethlehem, Pennsylvania. The work \emph{Scheduling elective surgeries under uncertainty: a multi-objective stochastic approach} presented here got the second place out of 13 submissions at the 14th AIMMS-MOPTA Optimization Modeling Competition. 
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Journal Articles}
\begin{itemize}
    \item[\texttt{[J2]}] Bernardelli, A. M., Gualandi, S., Milanesi, S., Lau, H. C., Yorke-Smith, N. (2024). Multiobjective Linear Ensembles for Robust and Sparse Training of Few-Bit Neural Network. INFORMS Journal on Computing.
    \item[\texttt{[J1]}] Bernardelli, A.M., Bonasera, L., Duma, D., Vercesi, E. (2024). Multi-objective stochastic scheduling of inpatient and outpatient surgeries. Flex Serv Manuf J. 
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Conference Proceedings}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{[P1]}] Bernardelli, A.M., Gualandi, S., Lau, H.C., Milanesi, S. (2023). The BeMi Stardust: A Structured Ensemble of Binarized Neural Networks. In: Sellmann, M., Tierney, K. (eds) Learning and Intelligent Optimization. LION 2023. Lecture Notes in Computer Science, vol 14286. Springer, Cham.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Preprints}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{[A3]}] Riccardi, G., Bernardelli, A. M., Gualandi, S. (2026). Theoretical Perspectives on Jabr-Type Convex Relaxations for AC Optimal Power Flow. arXiv preprint arXiv:2604.00664. Currently under revision at European Journal of Operational Research.
    \item[\texttt{[A2]}] Sosso, A., Bernardelli, A. M., Gualandi, S. (2025). The Cloven Traveling Salesman: Cycle Covers and the Integrality Gap of Small ATSP Instances. arXiv preprint arXiv:2511.05045. Accepted at Optimization Letters, to appear.
    \item[\texttt{[A1]}] Bernardelli, A. M., Vercesi, E., Gualandi, S., Mastrolilli, M., Gambardella, L. M. (2024). Lower bounds for the integrality gap of the bi-directed cut formulation of the Steiner Tree Problem. arXiv preprint arXiv:2405.13773. Currently under revision at Discrete Applied Mathematics.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Awards}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{04/2023}] Grant awarded by the TAILOR Connectivity Fund for a one-month visiting period at TU Delft, Delft, The Netherlands.
    \item[] 
    \item[\texttt{07/2022}] 2nd place out of 13 submissions at the 14th AIMMS-MOPTA Optimization Modeling Competition.
    \item[]
    \item[\texttt{09/2019}] Department scholarship for the Master’s degree program in Mathematics. 
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Visiting Periods}
\begin{itemize}[labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{09/2023-02/2024}] I spent six months in USI (Università della Svizzera italiana), Lugano, Switzerland, as part of my Ph.D. joint program, working on integrality gap problems with Professor Luca Maria Gambardella.
    \item[\texttt{04/2023}] I spent one month in TU Delft, Delft, The Netherlands, as a guest of STAR Lab, working on AI and optimization with Dr. Neil Yorke-Smith.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conference Organization}
\begin{itemize}[labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{05/2025}] I was one of the organizers of the COMPMAT Spring Workshop 2025, that was held at University of Pavia on May 23, 2025.
    \item[\texttt{02/2025}] I was part of the organizing committee of the 9th AIROYoung Workshop, that was held at University of Pavia from the 26th to the 28th of February, 2025.
    \item[\texttt{2022-2024}] I was a co-organizer of Caffè Beltrami, a cycle of seminars aimed at introducing different areas of research in mathematics to Bachelor’s and Master’s students.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Teaching Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Teaching}
\begin{itemize}[noitemsep, labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{2024/2025}] 511180 -- Algorithms for Optimization ([LM-16] Finance), University of Pavia, 22 hours. Co-teaching with Prof. Daniele Boffi, who held the other 22 hours of the course.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Supervising}
\begin{itemize}[labelwidth=*,align=left, labelwidth=!]
    \item[\texttt{2024/2025}] \emph{Riduzione delle Emissioni di Carbonio mediante Ottimizzazione Stocastica dello Stoccaggio Energetico a Batteria in Sistemi Fotovoltaici}, Anna Sacilotto, Master’s Thesis in Mathematics at University of Pavia, co-supervised with Prof. Stefano Gualandi.
    \item[\texttt{2024/2025}] \emph{Strengthening the SOCP formulation for the ACOPF problem}, Arthur Mazeyrat, Master's Report in Operations Research and Combinatorial Optimization at University Grenoble Alpes, co-supervised with Prof. Stefano Gualandi and Gabor Riccardi.
    \item[\texttt{2023/2024}] \emph{The Cloven Travelling Salesman: a new Approach to the ATSP Integrality Gap Estimation}, Alessandro Sosso, Master’s Thesis in Mathematics at University of Pavia, co-supervised with Prof. Stefano Gualandi.
    \item[\texttt{2022/2023}] \emph{On the exactness of Jabr-like models and distributionally robust stochastic optimal power flow}, Gabor Riccardi, Master’s Thesis in Mathematics at University of Pavia, co-supervised with Prof. Stefano Gualandi.
    \item[\texttt{2022/2023}] \emph{Analisi di architetture per Binarized Neural Networks}, Andrea Panno, Bachelor’s Thesis in Bioengineering at University of Pavia, co-supervised with Prof. Stefano Gualandi and Simone Milanesi.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Tutoring}
\begin{itemize}[,align=left, labelwidth=!]
    \item[\texttt{2021/2022}] Tutoring activity for the course \emph{Geometria e Algebra} that was held by prof. Francesco Bonsante for the Bachelor’s degree program \emph{Bioingegneria} at University of Pavia. 40 hours.
    \item[\texttt{2021/2022}] Tutoring activity for first-year students attending the Bachelor’s degree program in Mathematics at the University of Pavia. 40 hours.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Personal Information}
\begin{itemize}[leftmargin=0pt]
    \item[] Date of birth: 19/07/1997
    \item[] e--mail address: \texttt{ambrogiomaria.bernardelli(at)unipv.it}
    \item[] Phone number: +39 339 2001516
    \item[] Personal webpage: \href{https://ambrogiomb.github.io/}{\texttt{ambrogiomb.github.io}}
    \item[] ORCID: \href{https://orcid.org/0000-0002-2328-7062}{0000-0002-2328-7062}
    \item[] Research group website: \href{https://www.compopt.it/}{\texttt{compopt.it}}
\end{itemize}
\vfill
\begin{center}
    \small\texttt{Last updated: \today}
\end{center}
\end{document}

